% !TeX spellcheck = en_US

\chapter{Design overview}


\section{Activities}
The application will be designed for usage in portrait mode on hand-held devices, as well as landscape mode on larger devices e.g. tablets. Since the layout changes, the design of the application also changes to a large degree, in order to deliver the best possible user flow in each case.

\subsection{Portrait}
I portrait mode we will have the following activities:
\begin{itemize}
	\item Setup/options screen
	\item Map mode (Default)
	\item List mode
	\item Show prices
	\item Route mode
	\item Report prices
	\item View ledger
	\item Enter ledger information
\end{itemize}

\subsection{Landscape}
In landscape mode, the dynamics of user operation has changed, and we will instead use fragments to alter the content of our activities depending on the user action. Thus, we have a different list of activities here:
\begin{itemize}
	\item Setup/options screen
	\item Main screen
	\item View ledger
\end{itemize}

Here, the main screen is split into two pieces, each showing a different fragment. For instance, it could be the map mode from portrait on the left side, and the right side would show the prices for the last selected station. The map mode could be swapped for the list view while still keeping the prices list. While at a station, the show prices fragment could be replaced by a report prices fragment. When planning a route, the map fragment would be shown in unison with the route mode fragment.

\section{Risks}
A high degree of fragmentation between the portrait and landscape modes.
The requirement for backend API.
The acquisition of data.