% !TeX spellcheck = en_US

\chapter{User stories}
Here follows a list of user stories, outlining the intended features and functionality of the application.

\section{Setup}
\begin{itemize}
	\item As a user,
	\item I expect the application to know my default gas type,
	\item so it can guide me to the best prices.
\end{itemize}
As a user, I expect the application to know my default gas type, so it can guide me to the best prices.

At first run, the application shows a setup screen. Here, the user selects the default type of gas to use in the application.

\section{Fill up gas}
As a user, I wish to find the cheapest gas in my vicinity.

In the default view, a map is shown centered on the users current location, showing the nearest gas stations and the price for the default gas type.

As a user, I wish to be guided to my selected gas station, so I can take advantage of the low prices.

Once the user has selected a gas station, navigation directions is show in the default navigation provider.

As a user, I wish to know my fuel consumption better, to monitor my driving and the health of my vehicle.

When the user has been stationary at a gas station for two minutes, a notification is shown prompting the user to enter information about gas price and amount, to store in an ledger.

As a application owner, I wish to have the most up to date information, so more people can take advantage of the application.

If the user enters information about fuel price and amount, the price is sent to the remote server, to update the current prices for all users.